---
title: "Problem5_BubbleSort"
author: "Akira MATSUI"
date: "March 27, 2017"
output: pdf_document
---


# Introduction
In this section, we will learn "[Bubble Sort](https://en.wikipedia.org/wiki/Bubble_sort)" which is the one of the famous algorithms. Here is the simple explanation. 

There is a list that has some number.

`(2,7,1,6)`

What you need to do is to put these number in numerical order. Bubble sort is a method to do that by comparing each pair of adjacent items and swapping them if they are in the wrong order.

### First Step

`(2,1,7,6)`

### Second Step

`(1,2,6,7)`

On this example, the list is ordered in numerical order in second step. This algorithms is terminated when we do no change any number in that step.


# Question

- you have `BS <- as.integer( runif(100, min = 1, max = 99) )`
- Imprement `bubble sort` make `BS` to be sorted

## Sample Answer

```{r}
 bubble<- function(BS){
     N <- length(BS) #Number of factor
     flag = TRUE
     while(flag){
       flag = FALSE
       for (i in 2:N-1){
         if(BS[i] > BS[i+1]){
           B = BS[i]
           S = BS[i+1]
           BS[i] = S
           BS[i+1] = B
           flag = TRUE
          }
        }
     }
     return(BS)
 }
 BS <- as.integer( runif(100, min = 1, max = 99) )
 print("##########################BEFORE#########################################")
 print(BS)
 print("##########################AFTER#########################################")
 bubble(BS)
```



## swap function
If you want to use `swap()` function, "seqinr" library provide it.


```{r, eval=FALSE}
install.packages("seqinr")
```


```{r}
 bubble<- function(BS){
     library(seqinr)
     N <- length(BS) #Number of factor
     flag = TRUE
     while(flag){
       flag = FALSE
       for (i in 2:N-1){
         if(BS[i] > BS[i+1]){
           swap(BS[i],BS[i+1])
           flag = TRUE
          }
        }
     }
     return(BS)
 }
 BS <- as.integer( runif(100, min = 1, max = 99) )
 print("##########################BEFORE#########################################")
 print(BS)
 print("##########################AFTER#########################################")
 bubble(BS)
```






